\textbf{Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata}

### 2023-06-01 manuscript_v5/02-methods.qmd
map updated, majority of changes made

```{r,map}
#| label: fig-map
#| fig-cap: "Geographic representation of the data collected by the _Survey of COVID-19 related Behaviours and Attitudes_, collected by the Fields Institute in Ontario. The municipalities from where survey participants provided answers appear as points. The Health six Regions are color-coded. Internal boundaries within certain Health Regions indicate areas that belonged to the Local Integrated Health Networks (LHINs), the geographic areas for healthcare in Ontario before the adoption of the Health Regions."
#| message: false
#| echo: false
#| out-height: 100%

knitr::include_graphics(here("data","map_data","map_cairo.pdf"))

>>>>

```{r,map}
#| label: fig-map
#| fig-cap: "Geographic representation of the data collected by the _Survey of COVID-19 related Behaviours and Attitudes_, collected by the Fields Institute in Ontario. Municipalities from where survey participants provided answers appear as points, color indicates number of observation obtained from each city. The Health six Regions are color-coded and labelled sequentially. Internal boundaries within certain Health Regions indicate areas previously covered by the Local Integrated Health Networks (LHINs)."
#| message: false
#| echo: false
#| out-height: 100%
#| out-width: 100%

knitr::include_graphics(here("data","map_data","map_June_01.pdf"))

### 2023-06-01 manuscript_v5/main.qmd
map updated, majority of changes made

---
title: '**Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata**'
author:
  - name: Ariel Mundo Ortiz
    affil-id: 1,2,3
  - name: Bouchra Nasri
    affil-id: 1,2,3,\*
affiliations: 
  - id: 1
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: 2
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada
  - id: 3
    name: Centre de recherche en santé publique, University of Montreal, Montréal, Canada
  - id: \*
    name: Corresponding author, \url{bouchra.nasri@umontreal.ca}
format: 
  pdf:
    keep-tex: true
    template-partials: 
      - latex/title.tex
    include-in-header:
      - text: |
         \usepackage[noblocks]{authblk}
         \renewcommand*{\Authsep}{, }
         \renewcommand*{\Authand}{, }
         \renewcommand*{\Authands}{, }
         \renewcommand\Affilfont{\small}
      - file: latex/preamble.sty
# authors:
#   - name: Ariel Mundo Ortiz
#     affiliations:
#       - ref: crm
#       - ref: espum
#     email: ariel.mundo.ortiz@umontreal.ca
#     orcid: 0000-0002-6014-4538
#   - name: Bouchra Nasri
#     affiliations:
#       - ref: crm
#       - ref: espum
#     email: bouchra.nasri@umontreal.ca
#     corresponding: true
# affiliations:
#   - id: crm
#     name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
#   - id: espum
#     name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
# filters:
#   - authors-block
# format: 
#   pdf:
    # include-in-header:
    #   - text: |
    #       \usepackage{rotfloat}
    #   - file: latex/preamble.sty
    # #mainfont: "Palatino Linotype"
    # keep-tex: true
    link-citations: true #adds links to the citations
#linestretch: 1
bibliography: references/refs.bib
csl: references/jama.csl

>>>>

---
title: '**Differences in COVID-19 vaccination in the province of Ontario across Health Regions and socio-economic strata**'
author:
  - name: Ariel Mundo Ortiz
    affil-id: 1,2,3
  - name: Bouchra Nasri
    affil-id: 1,2,3,\*
affiliations: 
  - id: 1
    name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
  - id: 2
    name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada
  - id: 3
    name: Centre de recherche en santé publique, University of Montreal, Montréal, Canada
  - id: \*
    name: Corresponding author, \url{bouchra.nasri@umontreal.ca}
format: 
  pdf:
    geometry:
      - top=20mm
      - left=20mm
      - right=20mm
      - bottom=20mm
    keep-tex: true
    template-partials: 
      - latex/title.tex
    include-in-header:
      - text: |
         \usepackage[noblocks]{authblk}
         \renewcommand*{\Authsep}{, }
         \renewcommand*{\Authand}{, }
         \renewcommand*{\Authands}{, }
         \renewcommand\Affilfont{\small}
      - file: latex/preamble.sty
# authors:
#   - name: Ariel Mundo Ortiz
#     affiliations:
#       - ref: crm
#       - ref: espum
#     email: ariel.mundo.ortiz@umontreal.ca
#     orcid: 0000-0002-6014-4538
#   - name: Bouchra Nasri
#     affiliations:
#       - ref: crm
#       - ref: espum
#     email: bouchra.nasri@umontreal.ca
#     corresponding: true
# affiliations:
#   - id: crm
#     name: Centre de Recherches Mathématiques, University of Montreal, Montréal, Canada
#   - id: espum
#     name: Department of Social and Preventive Medicine, École de Santé Publique, University of Montreal, Montréal, Canada 
# filters:
#   - authors-block
# format: 
#   pdf:
    # include-in-header:
    #   - text: |
    #       \usepackage{rotfloat}
    #   - file: latex/preamble.sty
    # #mainfont: "Palatino Linotype"
    # keep-tex: true
    link-citations: true #adds links to the citations
#linestretch: 1
bibliography: references/refs.bib
csl: references/jama.csl

### 2023-06-01 manuscript_v5/main.tex
map updated, majority of changes made

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\date{}
\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt, enhanced, interior hidden]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics[width=\textwidth,height=1\textheight]{../data/map_data/map_cairo.pdf}

@@

\caption{\label{fig-map}Geographic representation of the data collected
by the \emph{Survey of COVID-19 related Behaviours and Attitudes},
collected by the Fields Institute in Ontario. The municipalities from
where survey participants provided answers appear as points. The Health
six Regions are color-coded. Internal boundaries within certain Health
Regions indicate areas that belonged to the Local Integrated Health
Networks (LHINs), the geographic areas for healthcare in Ontario before
the adoption of the Health Regions.}

@@

Finally, \textbf{the place of habitation affected the odds of
vaccination for certain underrepresented groups, as significantly lower
odds of vaccination were identified for the interaction between Health
Region and race} in the case of Black individuals in the Central Health
Region (OR=0.39, CI={[}0.2,0.75{]}), Arab/Middle Eastern individuals in
the East Health Region (OR=0.41 {[}0.17, 0.98{]}), and in the Indigenous
and mixed groups in the West Health Region (ORs and CIs={[}0.31 {[}0.14,
0.7{]} and 0.38 {[}0.19, 0.76{]}, respectively).

@@

In this study, we hypothesized that differences in COVID-19 vaccination
uptake were present between the Health Regions between late 2021 and
early 2022. Our goal was to determine which socio-demographic groups
could be impacted by these disparities in order to provide
decision-makers with information that could be used to develop policies
focused on reducing or eliminating these differences and ensure that the
Health Region model is able to fulfill its mission of improving health
access for all Ontarians. \textbf{making corrections up to this point}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=20mm,left=20mm,right=20mm,bottom=20mm]{geometry}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\date{}
\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, sharp corners, borderline west={3pt}{0pt}{shadecolor}, interior hidden, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics[width=1\textwidth,height=1\textheight]{../data/map_data/map_June_01.pdf}

@@

\caption{\label{fig-map}Geographic representation of the data collected
by the \emph{Survey of COVID-19 related Behaviours and Attitudes},
collected by the Fields Institute in Ontario. Municipalities from where
survey participants provided answers appear as points, color indicates
number of observation obtained from each city. The Health six Regions
are color-coded and labelled sequentially. Internal boundaries within
certain Health Regions indicate areas previously covered by the Local
Integrated Health Networks (LHINs).}

@@

Finally, the place of habitation affected the odds of vaccination for
certain underrepresented groups, as significantly lower odds of
vaccination were identified for the interaction between Health Region
and race in the case of Black individuals in the Central Health Region
(OR=0.39, CI={[}0.2,0.75{]}), Arab/Middle Eastern individuals in the
East Health Region (OR=0.41 {[}0.17, 0.98{]}), and in the Indigenous and
mixed groups in the West Health Region (ORs and CIs={[}0.31 {[}0.14,
0.7{]} and 0.38 {[}0.19, 0.76{]}, respectively).

@@

In this study, we hypothesized that differences in COVID-19 vaccination
uptake were present between the Health Regions between late 2021 and
early 2022. Our goal was to determine which socio-demographic groups
could be impacted by these disparities in order to provide
decision-makers with information that could be used to develop policies
focused on reducing or eliminating these differences and ensuring that
the Health Region model is able to fulfill its mission of improving
health access for all Ontarians.
